A User-Extensible and Adaptable Parser Architecture

### 2008-12-12 doc/sgai-2008-slides.tex
Final changes before presentation.

\newcommand{\timingnote}[1]{%
    \textbf{#1}%
}

@@

        \item Postfix log lines change over time and from site to site, so
            it must be easy for the end user to parse new log lines.

@@

        \item By separating parsing of log lines from processing of log
            lines, we can make parsing new or changed log lines as easy as
            possible, while still allowing for complicated processing when
            necessary.

@@

    The parser architecture is divided into three parts: Framework,
    Actions, and Rules.

@@

        \item [Framework] The framework manages rules, manages the parsing
            process, and provides support functions to actions.  For each
            input log line, the framework tries each rule in turn until one
            matches, then it invokes the action specified by the matching
            rule.

@@

        \item The architecture can be used when parsing input files that
            are not completely understood or that do not have 100\% parsing
            coverage.  \timingnote{Emphasise this.}

@@

        \item Rules can be added, changed, or removed by actions while the
            parser is running, allowing dynamically changing parsing, e.g.\
            macros.  \timingnote{Currying functions in a calculator might
            be a good example.}

@@

        \item 115 (now 169) rules parsing 93 (now 522) contiguous log
            files: the 10 most frequently matching rules match 85.03\% of
            the log lines, the remainder tail off similar to a Power Law
            distribution.

        \item 18 actions; 15 are triggered by only one or two rules.
            \timingnote{client connecting, postfix reloading}

        \item 3 actions are triggered by an average of 50 rules:
            uninteresting (41), save\_data (49), and delivery\_rejected
            (59).
            %\timingnote{build/stats-action-distribution:}

@@

        \item Rules are sorted by how frequently they match, resulting in a
            mean reduction of 14.78\% in parsing time.  Priority attribute
            can be used to override this.  \timingnote{change in ordering
            is informative.  Described in paper}

@@

        \item Parsing time scales linearly with input size, but
            \textit{is\/} affected by input log lines: the log lines
            determine the number of rules used and the actions that will
            run, and some actions take longer to run than others.

@@

        \item Data mining to determine how well each anti-spam technique
            works.

        \item Data mining to search for combinations of features which can
            be used to detect spam, and development of new anti-spam
            techniques to defeat such spam.

@@

        \item Use Machine Learning techniques instead of writing rules;
            Instance Based Learning techniques must be used due to the size
            of the data set.  This is one use of the ability to add or
            change rules at run-time.  \timingnote{Compare to SLCT-based
            tool.}

>>>>

\newcommand{\timingnote}[1]{%
    %\textbf{#1}%
}

@@

        \item Postfix log lines change over time and from site to site, so
            it must be easy for the end user to parse new or changed log
            lines.

@@

        \item By separating parsing of log lines from processing of log
            lines, we can make parsing new or changed log lines as easy as
            possible, while still allowing for complex processing when
            necessary.

@@

    The parser architecture is divided into three parts: \newline{}
    Framework, Actions, and Rules.

@@

        \item [Framework] The framework manages rules, manages the parsing
            process, and provides support functions to actions.  \newline{}
            For each input log line, the framework tries each rule in turn
            until one matches, then it invokes the action specified by the
            matching rule.

@@

        \item The architecture can be used when parsing input files that
            are not completely understood or do not have 100\% parsing
            coverage.  \timingnote{Emphasise this.}

@@

        \item Rules can be added, changed, or removed by actions while the
            parser is running, allowing dynamically changing parsing.
            \timingnote{Currying functions in a calculator might be a good
            example.}

@@

        \item 115 (now 169) rules parsing 93 (now 522) contiguous log
            files: the 10 most frequently matching rules match 85.03\% of
            the log lines, the remaining rules tail off similar to a Power
            Law distribution.

        \item 18 actions, of which 15 are triggered by only one or two
            rules.  \timingnote{client connecting, postfix reloading}

        \item 3 actions are triggered by a high number of rules:
            uninteresting~(41), save\_data~(49), and
            delivery\_rejected~(59).
            %\timingnote{build/stats-action-distribution:}

@@

        \item Rules are sorted by how frequently they match, resulting in a
            mean reduction of 14.78\% in parsing time.  A priority
            attribute can be used to override this.  \timingnote{change in
            ordering is informative.  Described in paper}

@@

        \item Parsing time scales linearly with input size, but
            \textit{is\/} affected by input log lines: the log lines
            determine the number of rules used and the actions that run,
            and some actions take longer to run than others.

@@

        \item Data mining to determine how effective each of the anti-spam
            techniques we currently use is.

        \item Data mining to search for combinations of features which can
            be used to detect spam, and development of new anti-spam
            techniques to reject such spam.

@@

        \item Use Machine Learning techniques instead of writing rules by
            hand; Instance Based Learning techniques must be used due to
            the size of the data set.  This is one potential use of the
            ability to add or change rules at run-time.
            \timingnote{Compare to SLCT-based tool.}
